Iterative construction of replicated designs based on Sobol' sequences

### 2016-06-10 crass/crassnew.tex
Changes in crassnew.tex

% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath,amssymb}
\usepackage{graphicx}

@@

\selectlanguage{francais}
% Text of abstract in French
\noindent{\bf R\'esum\'e} \vskip 0.5\baselineskip \noindent
{ \bf Construction de plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.}
%{\bf Plans r\'epliqu\'es \`a base de s\'equences de Sobol' pour estimer les effets principaux des param\`etres d'un mod\`ele. }
Dans l'objectif d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire it\'erativement des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'. Les propri\'et\'es de remplissement de l'espace des plans construits sont \'etudi\'ees sur la base de deux crit\`eres.
{\it Pour citer cet article~: L. Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
Paris, Ser. I 340 (2005).}
\end{abstract}
\end{frontmatter}
\selectlanguage{english}
\section{Introduction}
Mathematical models often involve a substantial number of poorly known parameters. The effect of these parameters on the output of the model can be assessed through sensitivity analysis. Global sensitivity analysis methods are useful tools to identify the parameters having the most influence on the output. A well known approach is the variance based method introduced by Sobol' in \cite{Sobol2}. This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model input. Among all Sobol' indices, one can distinguish first-order indices that estimate the main effect of each input.

The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension. %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.  
 An elegant solution to reduce this cost relies on the construction of particular designs of experiments called replicated designs. The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}. 
Below we define replicated designs in a wider framework:

\begin{definition}%[Replicated designs]
\label{rep.designs}
Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$ and $\mathcal{D}=\{1,\dots,s\}$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
$[0,1)^{s}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a$ if $\forall \ u \subsetneq \mathcal{D}$ of cardinality $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
\end{definition}

The replication procedure introduced in \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$. This procedure has the major advantage of reducing the estimation cost as the number of model evaluations (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension. However, Sobol' indices estimates may still not be accurate enough if the input space is not properly explored.

@@

In this note, we propose the construction of two replicated point sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$. These two designs ensure that the input space is properly explored and can be used within the replication procedure to estimate all main-effects of a numerical model. The construction of the two replicated designs is recursive, at each step each design is refined with a new set of points.

We first provide a brief introduction on digital sequences and then present two iterative approaches to construct the two replicated point sets. We end this note by studying the space-filling aspect of the two designs constructed.

@@

%The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the $(t,m,s)$-net definition as follows:
$(t,m,s)$-nets are defined as follows:

@@

By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limit case where $m\rightarrow\infty$, we can define $(t,s)$-sequences as:
\begin{definition}%[$(t,s)$-sequence]
For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
\end{definition}

Replicated design properties can apply to digital sequences. Therefore, we introduce the definition,
\begin{definition}
Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are \emph{digitally replicated} of order $a$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $a$.
\end{definition}

@@

$s$-dimensional Sobol' sequences are digital sequences designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over the Galois field $\mathbb{F}_2:=\{0,1\}$. We will denote by $\oplus$ the addition in $\mathbb{F}_2$. These generating matrices are recursively constructed through primitive polynomials and initial directional numbers. In \cite{Kuo}, Kuo and Joe detail this construction and also suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.

Consider the generating matrices $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$. Although $C_1,\dots,C_s$ are of infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points: for each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
\begin{equation}
\label{dig.net.eq.}
(x_{i,j,1},\dots,x_{i,j,m})^\intercal = C_j^{m} \vi,\qquad j= 1,\dots,s\, ,
\end{equation}
where $x_{i,j} = \sum_{k \geq 1}^m x_{i,j,k}2^{-k}$ is the binary expansion of $x_{i,j}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ is the vector obtained from the binary expansion of $i= \sum_{k \geq 0}^{m-1} i_{k}2^{k}$. All matrix operations are performed in $\mathbb{F}_2$. Below we provide an example on how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$,
\begin{equation*}
\begin{pmatrix}
x_{11,1,1} \\
x_{11,1,2} \\
x_{11,1,3} \\
x_{11,1,4}
\end{pmatrix} = 
\overbrace{
\begin{pmatrix}
1 & 0 & 0 & 0 \\
0 & 1 & 0 & 0 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{pmatrix}}^{C_1^4}
\overbrace{
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}}^{\bvec{11}}=
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}
,\qquad
\begin{pmatrix}
x_{9,2,1} \\
x_{9,2,2} \\
x_{9,2,3} \\
x_{9,2,4}
\end{pmatrix} = 
\overbrace{\begin{pmatrix}
1 & 1 & 1 & 1 \\
0 & 1 & 0 & 1 \\
0 & 0 & 1 & 1 \\
0 & 0 & 0 & 1
\end{pmatrix}}^{C_2^4}
\overbrace{\begin{pmatrix}
1 \\
0 \\
0 \\
1
\end{pmatrix}}^{\bvec{9}} =
\begin{pmatrix}
0 \\
1 \\
1 \\
1
\end{pmatrix}
\end{equation*}

To compute the next $2^m$ points of the sequence, one can infer from Equation (\ref{dig.net.eq.}) that \\$(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m+1})^\intercal=(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m},0)^\intercal\oplus {(c_j^{m+1})}^\intercal$, where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.

@@

In this section we propose two different approaches to iteratively construct two replicated point sets, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, based on Sobol' sequences. These two constructions are carried out according to the following recursive scheme :
$$\left\lbrace \begin{array}{l}
\mathcal{P}_0= B_0 \\
\mathcal{P}_\ell= \mathcal{P}_{\ell-1} \cup B_\ell \end{array}\right. \,
\hspace*{0.5cm}
\left\lbrace \begin{array}{l}
\mathcal{P}'_0= {B'}_0 \\
\mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right. 
$$
%$$\mathcal{P}_m= B_0 \cup \dots \cup B_m\, ,$$
%$$\mathcal{P}'_m= {B'}_0 \cup \dots \cup {B'}_m\, ,$$
where $B_\ell$ and $B'_\ell$, $\ell \geq 0$, are new sets of points added at step $\ell$ to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$. For all $\ell$, $\mathcal{P}_\ell$ and $\mathcal{P'}_\ell$ are two replicated designs of order $1$.

The first approach is called multiplicative because $|P_\ell|=2^\ell$ while the second one with $|P_\ell|=\ell|B_0|$ is called additive. In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}. However, for the additive case, we will consider an initial set of Sobol' points and apply different scramblings and digital shifts to extend the point sets. Additionally, in both cases one can randomize the points with Owen's scrambling \cite{OwenScrambling} as long as same coordinates of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ share the same scrambling.

@@

Two replicated point sets of order 1 $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ can be constructed using two $s$-dimensional Sobol' sequences. We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$. To insure that $2$-dimensional projections between $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other. Our choice of the $2s$ generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}.
\bigskip

In order to recursively construct designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, one just needs to compute $B_\ell=\{\vx_{2^{\ell-1}},\dots,\vx_{2^\ell-1}\}$ and ${B'}_\ell=\{\vx'_{2^{\ell-1}},\dots,\vx'_{2^\ell-1}\}$ at each step $\ell \geq 1$ to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$, starting with $B_0=B'_0=\{\bvec{0}\}$ where $\bvec{0}$ denotes the null vector. Each set $B_\ell$ can be obtained applying equation (\ref{dig.net.eq.}) to $C_1,\dots,C_s$ and likewise for ${B'}_\ell$ using $C'_1,\dots,C'_s$.

@@

With the multiplicative approach, the size of designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ is multiplied by $2$ each time $\ell$ is increased by one. This growth rate may be inadequate for some applications. The additive approach presented in this section is attractive due to a slower size growth. Given an initial choice of $r\geq 1$ that specifies the size of $B_0$ and ${B'}_0$, only $|B_0|=2^r$ points are added to both designs at each step. The main drawback of this approach is that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ do not possess the structure of a Sobol' sequence anymore when $m\geq 1$. Still, both designs display good space-filling properties as shown in the next section.

@@

The two replicated point sets $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ constructed with the additive approach are iteratively refined with $B_\ell$ and ${B'}_\ell$. Each $B_\ell$ and ${B'}_\ell$ are $(t,r,s)$-nets. First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are set to be the first $2^r$ Sobol' points of two $s$-dimensional sequences. The generating matrices of these two sequences are selected as in the multiplicative approach. Then, $B_\ell$ (resp. ${B'}_\ell$), for $\ell \geq 1$, is obtained from $B_0$ (resp. ${B'}_0$) by carrying out digital shifts and scrambling operations. These operations guarantee that both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial sets $B_0$ and ${B'}_0$. We detail below the construction of $B_\ell$ and ${B'}_\ell$.
\bigskip

At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated as follows:

for each $i=0,\dots,2^r-1$, points $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ are obtained by:
\begin{equation}
\label{dig.shift}
(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = L (x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ x_{i,j}^{(\ell)}=\sum_{k = 1}^r x_{i,j,k}^{(\ell)}2^{-k}$, $\ve_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and $L$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
\bigskip

Likewise ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained as follows: 
%from $B_\ell$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows

for each $i=0,\dots,2^r-1$, points ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ are obtained by:
\begin{equation}
\label{ibinom.scrambling}
({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = {L'} ({x'}_{i,j,1}^{(0)},\dots,{x'}_{i,j,r}^{(0)})^\intercal\oplus {\ve'}_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ {x'}_{i,j}^{(\ell)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(\ell)}2^{-k}$, ${\ve'}_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and ${L'}$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
\bigskip

The left multiplications carried out in Equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) by matrices $L$ and $L'$ are referred as random linear scrambling \cite{Matousek} while the additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts. There are exactly $2^r$ different choices for vectors $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices for matrices $L$ and $L'$. The vectors $\ve_j$ (resp. ${\ve}'_j$) are selected as follows:
\begin{itemize}
\item[i)] for the first coordinate, the same vector $\ve_1$ (resp. ${\ve}'_1$) is selected at each iteration $\ell$,
\item[ii)] for the others coordinates, the vectors $\ve_2,\dots,\ve_s$ (resp. ${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$. There exists exactly $2^{r (s-1)}$ combinations of this set which leaves us with a large panel of choice.
\end{itemize}

We have the following result:
%\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.

@@

It has already been pointed out in the previous section that the two replicated designs constructed with the additive approach loose their $(t,m,s)$-net properties once a new set of points is added. Nonetheless, they still retain space-filling properties that combined with the low cost of the additive approach make their use appealing. We propose two study the space-filling properties of the two designs constructed with both approaches: multiplicative and additive, based on two criteria.

>>>>

% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath,amssymb,color}
\usepackage{graphicx}

@@

\selectlanguage{francais}
% Text of abstract in French
\noindent{\bf R\'esum\'e} \vskip 0.5\baselineskip \noindent
{ \bf Construction de plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.}
%{\bf Plans r\'epliqu\'es \`a base de s\'equences de Sobol' pour estimer les effets principaux des param\`etres d'un mod\`ele. }
Dans l'objectif d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire it\'erativement des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'. Les propri\'et\'es de remplissement de l'espace des plans construits sont \'etudi\'ees sur la base de deux crit\`eres.
{\it Pour citer cet article~: L. Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
Paris, Ser. I 340 (2005).}
\end{abstract}
\end{frontmatter}
\selectlanguage{english}
\section{Introduction}
Mathematical models often involve a substantial number of poorly known parameters. The effect of these parameters on the output of the model can be assessed through sensitivity analysis. Global sensitivity analysis methods are useful tools to identify the parameters having the most influence on the output. A well known approach is the variance based method introduced by Sobol' in \cite{Sobol2}. This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model input. Among all Sobol' indices, one can distinguish the first-order indices that estimate the main effect of each input.

The procedure to estimate first-order Sobol' indices proposed by Sobol' and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive number of model evaluations that grows with respect to the input space dimension. %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.  
 An elegant solution to reduce this number relies on the construction of particular designs of experiments called replicated designs. The notion of replicated designs was first introduced by McKay through its definition of replicated Latin Hypercubes in \cite{Mckay}. Below we provide this definition in a more general framework:

\begin{definition}%[Replicated designs]
\label{rep.designs}
Consider $\vx \in [0,1)^s$, and $\vx_u \in [0,1)^{s-|u|}$ the subset of dimensions of $\vx$ given by $u\subsetneq \{1,\dots,s\}$, where $|u|$ is the cardinality of $u$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1)^{s}$, and denote by $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$) the subset of dimensions of points in $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a=1,\dots,s-1$, if for any $u\subsetneq \{1,\dots,s\}$ with $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
\end{definition}

The replication procedure described in \cite{Mara,Tissot} allows the estimation of all first-order Sobol' indices with only two replicated designs of order $1$. This procedure has the major advantage of reducing the number of model evaluations, evaluating only on designs $\mathcal{P}$ and $\mathcal{P}'$ regardless of the input space dimension. However, Sobol' indices estimates may still not be accurate enough if designs $\mathcal{P}$ and $\mathcal{P}'$ do not explore the input space properly.

@@

In this note, we propose two different constructions of replicated designs of order $1$ based on Sobol' sequences. These two constructions ensure that the input space is properly explored and can be used within the replication procedure to estimate all first order Sobol' indices. The definition of these constructions is recursive, therefore one can iteratively refine the replicated designs by adding the corresponding new set of points.

We first provide a brief introduction on digital sequences and then present two iterative approaches to construct the two replicated point sets. We end this note by analyzing the space-filling properties of the two designs constructed.

@@

%The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the $(t,m,s)$-net definition as follows:

@@

By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limit case where $m\rightarrow\infty$, we can define the $(t,s)$-sequence as:
\begin{definition}%[$(t,s)$-sequence]
For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
\end{definition}

The replicated design properties can also apply to digital sequences. Hence, we introduce the following definition,
\begin{definition}
Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are \emph{digitally replicated} of order $a$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $a$.
\end{definition}

@@

$s$-dimensional Sobol' sequences are digital sequences in base $b=2$ that can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over the Galois field $\mathbb{F}_2:=\{0,1\}$. We will denote by $\oplus$ the addition in $\mathbb{F}_2$. These generating matrices are recursively constructed given some primitive polynomials and initial directional numbers. In \cite{Kuo}, Kuo and Joe detail this construction and also suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.

Consider the generating matrices $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$. Although $C_1,\dots,C_s$ are of infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ Sobol' points: for each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
\begin{equation}
\label{dig.net.eq.}
(x_{i,j,1},\dots,x_{i,j,m})^\intercal = C_j^{m} \vi,\qquad j= 1,\dots,s\, ,
\end{equation}
where $x_{i,j} = \sum_{k \geq 1}^m x_{i,j,k}2^{-k}$ is the binary expansion of $x_{i,j}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ is the vector obtained from the binary expansion of $i= \sum_{k \geq 0}^{m-1} i_{k}2^{k}$. All matrix operations are performed in $\mathbb{F}_2$. Below we provide an example of how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$,
\begin{equation*}
\begin{pmatrix}
x_{11,1,1} \\
x_{11,1,2} \\
x_{11,1,3} \\
x_{11,1,4}
\end{pmatrix} = 
\underbrace{
\begin{pmatrix}
1 & 0 & 0 & 0 \\
0 & 1 & 0 & 0 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{pmatrix}}_{C_1^4}
\underbrace{
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}}_{\bvec{11}}=
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}
,\qquad
\begin{pmatrix}
x_{9,2,1} \\
x_{9,2,2} \\
x_{9,2,3} \\
x_{9,2,4}
\end{pmatrix} = 
\underbrace{\begin{pmatrix}
1 & 1 & 1 & 1 \\
0 & 1 & 0 & 1 \\
0 & 0 & 1 & 1 \\
0 & 0 & 0 & 1
\end{pmatrix}}_{C_2^4}
\underbrace{\begin{pmatrix}
1 \\
0 \\
0 \\
1
\end{pmatrix}}_{\bvec{9}} =
\begin{pmatrix}
0 \\
1 \\
1 \\
1
\end{pmatrix}
\end{equation*}

%\bigskip

To compute the next $2^m$ points of the sequence, one can infer from \eqref{dig.net.eq.} that
\begin{equation}\label{Sobol_iter_constr}
(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m+1})^\intercal=(x_{i,j,1},\dots,x_{i,j,m},0)^\intercal\oplus {(c_j^{m+1})}^\intercal,\quad i=0,\dots,2^m-1,
\end{equation}
where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.

@@

In this section we propose two different approaches to iteratively construct two replicated point sets, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, based on Sobol' sequences. These two constructions are carried out according to the following recursive scheme :
$$\left\lbrace \begin{array}{l}
\mathcal{P}_0= B_0 \\
\mathcal{P}_\ell= \mathcal{P}_{\ell-1} \cup B_\ell \end{array}\right. \,
\hspace*{0.5cm}
\left\lbrace \begin{array}{l}
\mathcal{P}'_0= {B'}_0 \\
\mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right. , 
\hspace*{0.5cm} \ell \geq 1,
$$
%$$\mathcal{P}_m= B_0 \cup \dots \cup B_m\, ,$$
%$$\mathcal{P}'_m= {B'}_0 \cup \dots \cup {B'}_m\, ,$$
where $B_\ell$ and $B'_\ell$ are new sets of points added at step $\ell$ to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$. For all $\ell\geq 0$, $\mathcal{P}_\ell$ and $\mathcal{P'}_\ell$ are two replicated designs of order $1$.

The first approach is called multiplicative because $|P_\ell|=2^\ell$ while the second one is called additive and $|P_\ell|=\ell|B_0|$. In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}. However, for the additive case, we will consider an initial set of Sobol' points and apply different scramblings and digital shifts to extend the point sets. Additionally, in both cases one can randomize the points using Owen's scrambling \cite{OwenScrambling} as long as same coordinates of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ share the same scrambling.

@@

Two replicated point sets of order 1, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, can be constructed using two $s$-dimensional Sobol' sequences. We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$. To ensure that the $2$-dimensional projections between $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other. Our choice of generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ is based on the results obtained by Joe and Kuo in \cite{Kuo}.
\bigskip

In order to iteratively extend designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, one just needs to compute $B_\ell=\{\vx_{2^{\ell-1}},\dots,\vx_{2^\ell-1}\}$ and ${B'}_\ell=\{\vx'_{2^{\ell-1}},\dots,\vx'_{2^\ell-1}\}$, starting with $B_0=B'_0=\{\bvec{0}\}$, with $\bvec{0}$ the null vector. Each set $B_\ell$ and ${B'}_\ell$ can be constructed using \eqref{Sobol_iter_constr} applied to $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$.

@@

With the multiplicative approach, the size of designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ is multiplied by $2$ each time $\ell$ is increased by one. This growth rate may be inadequate for some applications. The additive approach presented in this section is attractive due to a slower size growth. Given an initial choice of $r\geq 1$ that specifies the size of $B_0$ and ${B'}_0$, only $|B_0|=2^r$ points are added to both designs at each step. The main drawback of this approach is that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ do not inherit the structure of a Sobol' sequence when $\ell\geq 1$. Nevertheless, both designs display good space-filling properties as shown in the next section.

@@

Analogously to the multiplicative case, the two replicated point sets $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ constructed with the additive approach are iteratively refined with $B_\ell$ and ${B'}_\ell$. First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are set to be the first $2^r$ points of two $s$-dimensional Sobol' sequences. The generating matrices of these two sequences are selected as in the multiplicative approach. Then, $B_\ell$ (resp. ${B'}_\ell$), for $\ell \geq 1$, is obtained from $B_0$ (resp. ${B'}_0$) by carrying out digital shifts and scrambling operations. Therefore, both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial sets $B_0$ and ${B'}_0$. %We detail below the construction of $B_\ell$ and ${B'}_\ell$.
\bigskip

At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated as follows: for each $i=0,\dots,2^r-1$, point $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming $\vx_i^{(0)}$,
\begin{equation}
\label{dig.shift}
(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = L (x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ x_{i,j}^{(\ell)}=\sum_{k = 1}^r x_{i,j,k}^{(\ell)}2^{-k}$, $\ve_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and $L$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
\bigskip

Likewise, ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained as follows: for each $i=0,\dots,2^r-1$, point ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming ${\vx'}_i^{(0)}$,
%from $B_\ell$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows

\begin{equation}
\label{ibinom.scrambling}
({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = {L'} ({x'}_{i,j,1}^{(0)},\dots,{x'}_{i,j,r}^{(0)})^\intercal\oplus {\ve'}_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ {x'}_{i,j}^{(\ell)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(\ell)}2^{-k}$, ${\ve'}_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and ${L'}$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
\bigskip

Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts. There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$ {\color{blue} although ....... Because......., (I think it would be good to give the reason why a particular choice of $\ve_j$ needs to be made. Then, how)} vectors $\ve_j$ (resp. ${\ve}'_j$) are selected as follows:
\begin{itemize}
\item[i)] for the first dimension, the same vector $\ve_1$ (resp. ${\ve}'_1$) is selected at each iteration $\ell$,
\item[ii)] for the other dimensions, vectors $\ve_2,\dots,\ve_s$ (resp. ${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$. There exists exactly $2^{r (s-1)}$ combinations of this set which leaves us with a large panel of choice.
\end{itemize}

%We have the following result:
%\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.

@@

%In the previous section we showed how two replicated designs constructed with the additive approach are not $(t,m,s)$-nets after refinement. Nonetheless, they still retain space-filling properties that combined with the low iterative growth make their use appealing.
